\huge The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2021-05-18 Writeup/kohler_clarke_2021.tex
minor additional changes

In mathematical group theory, when the elements of one group is completely contained in another, the inner group is called a subgroup of the outer group \citep{RN1425}. The full list of subgroup relationships is listed in Section 1.4.2 of the Supplementary Material. Subgroup relationships between wallpaper groups can be distinguished by their indices. The index of a subgroup relationship is the number of cosets, i.e. the number of times the subgroup is found in the supergroup \citep{RN1425}. As an example, let us consider groups \textit{P2} and \textit{P6} \textcolor{ForestGreen}{(see Figure 1B)}. If we ignore the translations in two directions that both groups share, group \textit{P6} consists of the set of rotations \{$0^{\circ}$, $60^{\circ}$, $120^{\circ}$, $180^{\circ}$, $240^{\circ}$, $300^{\circ}$\}, in which \textit{P2} \{$0^{\circ}$, $180^{\circ}$\} is contained. \textit{P2} is thus a subgroup of \textit{P6}, and \textit{P6} can be generated by combining \textit{P2} with rotations \{$0^{\circ}$, $120^{\circ}$, $240^{\circ}$\}. Because \textit{P2} is repeated three times in \textit{P6}, \textit{P2} is a subgroup of \textit{P6} with index 3 \citep{RN1425}. \textcolor{ForestGreen}{Similarly, \textit{PMM} contains two reflections and rotations \{$0^{\circ}$, $180^{\circ}$\}. \textit{PMM} can be generated by adding an additional reflection to both \textit{P2} (\{$0^{\circ}$, $180^{\circ}$\}) and \textit{PM} (one reflection), so \textit{P2} and \textit{PM} are both subgroups of \textit{PMM} with index 2 (see Figure 1C).} The 17 wallpaper groups thus obey a hierarchy of complexity where simpler groups are subgroups of more complex ones \citep{RN1711}.

@@

Examples of the wallpaper groups and a summary of our brain imaging and psychophysical measurements are shown in Figure 2. For our primary SSVEP analysis, we only considered EEG data from a pre-determined region-of-interest (ROI) consisting of six electrodes over occipital cortex (see Supplementary Figure 1.1). SSVEP data from this ROI was filtered so that only the odd harmonics that capture the symmetry response contribute to the waveforms. While waveform amplitude is quite variable among the 16 groups, all groups have a sustained negative-going response that begins at about the same time for all groups, ~180 ms after the transition from the \textit{P1} control exemplar to the original exemplar. To reduce the amplitude of the symmetry-specific response to a single number that could be used in further analyses and compared to the psychophysical data, we computed the root-mean-square (RMS) over the odd-harmonic-filtered waveforms. The data in Figure 2 are shown in descending order according to RMS. The psychophysical results, shown in box plots in Figure 2, were also quite variable between groups, and there seems to be a general pattern where wallpaper groups near the top of the figure, that have lower SSVEP amplitudes, also have longer psychophysical threshold durations.

We now wanted to test our two hypotheses about how SSVEP amplitudes and threshold durations would follow subgroup relationships, and thereby quantify the degree to which our two measurements were consistent with the group theoretical hierarchy of complexity. We tested each hypothesis using the same approach. We first fitted a Bayesian model with wallpaper group as a factor and participant as a random effect. We fit the model separately for SSVEP RMS and psychophysical data and then computed posterior distributions for the difference between supergroup and subgroup. These difference distributions allowed us to compute the conditional probability that the supergroup would produce (a) larger RMS and (b) a shorter threshold durations, when compared to the subgroup. The posterior distributions are shown in Figure 3 for the SSVEP data, and in Figure 4 for the psychophysical data, which distributions color-coded according to conditional probability. For both data sets our hypothesis is confirmed: For the overwhelming majority of the 63 subgroup relationships, supergroups are more likely to produce larger symmetry-specific SSVEPs and shorter symmetry detection threshold durations, and in most cases the conditional probability of this happening is extremely high.

We also ran a control analysis using (1) odd-harmonic SSVEP data from a six-electrode ROI over parietal cortex (see Supplementary Figure 1.1) and (2) even-harmonic SSVEP data from the same occipital ROI that was used in our primary analysis. By comparing these two control analysis to our primary SSVEP analysis, we can address the specify of our effects in terms of location (occipital cortex vs parietal cortex) and harmonic (odd vs even). For both control analyses (plotted in Supplementary Figures 3.3 and 3.4), the correspondence between data and subgroup relationships was substantially weaker than in the primary analysis. We can quantify the strength of the association between the data and the subgroup relationships, by asking what proportion of subgroup relationships that reach or exceed a range of probability thresholds. This is plotted in Figure 5, for our psychophysical data, our primary SSVEP analysis and our two control SSVEP analyses. It shows that odd-harmonic SSVEP data from the occipital ROI and symmetry detection threshold durations both have a strong association with the subgroup relationships such that a clear majority of the subgroups survive even at the highest threshold we consider ($p(\Delta>0|data)>0.99$). The association is far weaker for the two control analyses.

@@

\textcolor{ForestGreen}{The current study uses 16 distinct wallpaper groups, while previous neuroimaging studies focused on a subset of 4 \citep{RN1725,RN1959}. This represents a significant conceptual advance, because it makes it possible to investigate the complete subgroup hierarchy among the 17 groups and ask to what extent the hierarchy is reflected in brain activity. Our data} provide a description of the visual system’s response to the complete set of symmetries in the two-dimensional plane. 
\textcolor{ForestGreen}{We do not} independently measure the response to \textit{P1}, but because each of the 16 other groups produce non-zero odd harmonic amplitudes (see Figure 2), we can conclude that the relationships between P1 and all other groups, where \textit{P1} is the subgroup, are also preserved by the visual system. The subgroup relationships are in many cases not obvious perceptually, and most participants had no knowledge of group theory. Thus, the visual system’s ability to preserve the subgroup hierarchy does not depend on explicit knowledge of the relationships. \textcolor{ForestGreen}{Previous brain-imaging studies have found evidence of parametric responses with the number of reflection symmetry folds \cite{keefe_2018, Sasaki_2005, makin_2016} and with the order of rotation symmetry \cite{RN1725}. Our study is the first demonstration that the brain encodes symmetry in this parametric fashion across every possible combination of different \textit{symmetry types}, and that this parametric encoding is also reflected in behavior.} Previous behavioral experiments have shown that although naïve observers can distinguish many of the wallpaper groups \citep{RN1253}, they tend to sort exemplars into fewer \textcolor{ForestGreen}{(4-12) sets than the number of wallpaper groups, often placing exemplars from different wallpaper groups in the same set \citep{RN172}. The two-interval forced choice approach we use in the current psychophysical experiment makes it possible to directly compare symmetry detection thresholds to the subgroup hierarchy, and reveals that not only can the 17 wallpaper groups be distinguished based on behavioral data, behavior largely follows the subgroup hierarchy.}

\textcolor{ForestGreen}{A large literature exists on the \textit{Sustained Posterior Negativity} (SPN), a characteristic negative-going waveform that is known to reflect responses to symmetry and other forms of regularity and structure \citep{makin_2016}. The SPN scales with the proportion of reflection symmetry in displays that contain a mixture of symmetry and noise \cite{makin_formation_2020, palumbo_scaling_2015}, and both reflection, rotation and translation can produce a measurable SPN \cite{makin_2013}. It has recently been demonstrated that a holographic model of regularity \citep{van_der_helm_1996}, can predict both SPN amplitude \citep{makin_2016} and perceptual discrimination performance \citep{nucci_2007} for dot patterns that contain symmetry and other types of regularity. The available evidence suggests that the SPN and our SSVEP measurements are two distinct methods for isolating the same symmetry-related brain response: When observed in the time-domain, the symmetry-selective odd-harmonic responses produce similarly sustained waveforms (see Figure 2), odd-harmonic SSVEP responses can be measured for dot patterns similar to those used to measure the SPN \citep{RN1954}, and the one event-related study on the wallpaper groups also found SPN-like waveforms \citep{RN1959}. Future work should more firmly establish the connection and determine if the SPN can capture similarly precise symmetry responses as the SSVEPs presented here. It would also be worthwhile to ask if and how \textit{W} can computed for our random-noise based wallpaper textures where combinations of symmetries tile the plane.}

We observe a reliable correlation between our brain imaging and psychophysical data. This suggests that the two measurements reflect the same underlying symmetry representations in visual cortex. \textcolor{ForestGreen}{It should be noted that the correlation is relatively modest ($R^2 = 0.44$). This may be partly due to the fact that different individuals participated in the two experiments. It may also be related to the fact that participants where not doing a symmetry-related task during the SSVEP experiment, but instead monitored the stimuli for brief changes in contrast that occured twice per trial (see Methods). Previous brain imaging studies have found enhanced reflection symmetry responses when participants performed a symmetry-related task \citep{makin_formation_2020, Sasaki_2005, keefe_2018}. It is possible that adding a symmetry-related task to our SSVEP experiment would have produced measurements that reflected subgroup relationships to an even higher extent than what we observed. On the other hand, our results are already close to ceiling (see Figure 5) and adding a symmetry-related task may simply enhance SSVEP amplitudes overall without improving the discriminality of individual groups, as has been observed for reflection by \cite{keefe_2018}. Task-driven processing may be important for detecting symmetries that have been subject to perspective distortion, as suggested by SPN measurements \citep{makin_conditions_2015} and somewhat less clearly in a subsequent functional MRI study \citep{keefe_2018}. Future work in which behavioral and brain imaging data are collected from the same participants, and task is manipulated in the SSVEP experiment, will help further establish the connection between the two measurements, and elucidate the potential contribution of task-related top-down processing to the current results.}

We also find an effect of index for both our brain imaging measurements and our symmetry detection thresholds. This means that the visual system not only represents the hierarchical relationship captured by individual subgroups, but also distinguishes between subgroups depending on how many times the subgroup is repeated in the supergroup, with more repetitions leading to larger pairwise differences. Our measured effect of index is relatively weak. This is perhaps because the index analysis does not take into account the \textit{type} of isometries that differentiate the subgroup and supergroup. The effect of symmetry type can be observed by contrasting the measured SSVEP amplitudes and detection thresholds for groups \textit{PM} and \textit{PG} in Figure 2. The two groups are comparable except \textit{PM} contains reflection and \textit{PG} contains glide reflection, and the former clearly elicits higher amplitudes and lower thresholds. An important goal for future work will be to map out how different symmetry types contribute to the representational hierarchy.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\linewidth]{../analysis/plots/model_roc_style.pdf}
\caption{This plot shows the proportion of subgroup relationships that satisfy \textcolor{ForestGreen}{$p(\Delta >0 | data) > x$ for the SSVEP data and $p(\Delta <0 | data) > x$ for the psychophysical data}. We can see that if we take $x = 0.95$ as our threshold, the subgroup relationships are preserved in 56/63 = 89\% and \textcolor{ForestGreen}{48/63 = 76\%} of the comparisons for the primary SSVEP and threshold duration datasets, receptively. This compares to the \textcolor{ForestGreen}{32/63= 51\%} and \textcolor{ForestGreen}{22/63 = 35\%} for the SSVEP control datasets.}
\label{fig:durations_rotations}
\end{figure}

@@

\subsection*{SSVEP Analysis}
Response waveforms were generated for each group by selective filtering in the frequency domain. For each participant, the average Fourier coefficients from the two sessions were averaged over trials and sessions. The SSVEP paradigm we used allowed us to separate symmetry-related responses from non-specific contrast transient responses. Previous work has demonstrated that symmetry-related responses are predominantly found in the odd harmonics of the stimulus frequency, whereas the even harmonics consist mainly of responses unrelated to symmetry, that arise from the contrast change associated with the appearance of the second image \citep{RN1954, RN1725}. This functional distinction of the harmonics allowed us to generate a single-cycle waveform containing the response specific to symmetry, by filtering out the even harmonics in the spectral domain, and then back-transforming the remaining signal, consisting only of odd harmonics, into the time-domain. For our main analysis, we averaged the odd harmonic single-cycle waveforms within a six-electrode region of interest (ROI) over occipital cortex (electrodes 70, 74, 75, 81, 82, 83). These waveforms, averaged over participants, are shown in Figure 2. The same analysis was done for the even harmonics and for the odd harmonics within a six electrode ROI over parietal cortex (electrodes 53, 54, 61, 78, 79, 86; see Supplementary Figure 1.1). The root-mean square values of these waveforms, for each individual participant, were used to determine whether each of the wallpaper subgroup relationships were preserved in the brain data.

>>>>

In mathematical group theory, when the elements of one group is completely contained in another, the inner group is called a subgroup of the outer group \citep{RN1425}. The full list of subgroup relationships is listed in Section 1.4.2 of the Supplementary Material. Subgroup relationships between wallpaper groups can be distinguished by their indices. The index of a subgroup relationship is the number of cosets, i.e. the number of times the subgroup is found in the supergroup \citep{RN1425}. As an example, let us consider groups \textit{P2} and \textit{P6} \textcolor{ForestGreen}{(see Figure \ref{fig:subgroups}B)}. If we ignore the translations in two directions that both groups share, group \textit{P6} consists of the set of rotations \{$0^{\circ}$, $60^{\circ}$, $120^{\circ}$, $180^{\circ}$, $240^{\circ}$, $300^{\circ}$\}, in which \textit{P2} \{$0^{\circ}$, $180^{\circ}$\} is contained. \textit{P2} is thus a subgroup of \textit{P6}, and \textit{P6} can be generated by combining \textit{P2} with rotations \{$0^{\circ}$, $120^{\circ}$, $240^{\circ}$\}. Because \textit{P2} is repeated three times in \textit{P6}, \textit{P2} is a subgroup of \textit{P6} with index 3 \citep{RN1425}. \textcolor{ForestGreen}{Similarly, \textit{PMM} contains two reflections and rotations \{$0^{\circ}$, $180^{\circ}$\}. \textit{PMM} can be generated by adding an additional reflection to both \textit{P2} (\{$0^{\circ}$, $180^{\circ}$\}) and \textit{PM} (one reflection), so \textit{P2} and \textit{PM} are both subgroups of \textit{PMM} with index 2 (see Figure \ref{fig:subgroups}C).} The 17 wallpaper groups thus obey a hierarchy of complexity where simpler groups are subgroups of more complex ones \citep{RN1711}.

@@

Examples of the wallpaper groups and a summary of our brain imaging and psychophysical measurements are shown in Figure \ref{fig:summary}. For our primary SSVEP analysis, we only considered EEG data from a pre-determined region-of-interest (ROI) consisting of six electrodes over occipital cortex (see Supplementary Figure 1.1). SSVEP data from this ROI was filtered so that only the odd harmonics that capture the symmetry response contribute to the waveforms. While waveform amplitude is quite variable among the 16 groups, all groups have a sustained negative-going response that begins at about the same time for all groups, ~180 ms after the transition from the \textit{P1} control exemplar to the original exemplar. To reduce the amplitude of the symmetry-specific response to a single number that could be used in further analyses and compared to the psychophysical data, we computed the root-mean-square (RMS) over the odd-harmonic-filtered waveforms. The data in Figure 2 are shown in descending order according to RMS. The psychophysical results, shown in box plots in Figure \ref{fig:summary}, were also quite variable between groups, and there seems to be a general pattern where wallpaper groups near the top of the figure, that have lower SSVEP amplitudes, also have longer psychophysical threshold durations.

We now wanted to test our two hypotheses about how SSVEP amplitudes and threshold durations would follow subgroup relationships, and thereby quantify the degree to which our two measurements were consistent with the group theoretical hierarchy of complexity. We tested each hypothesis using the same approach. We first fitted a Bayesian model with wallpaper group as a factor and participant as a random effect. We fit the model separately for SSVEP RMS and psychophysical data and then computed posterior distributions for the difference between supergroup and subgroup. These difference distributions allowed us to compute the conditional probability that the supergroup would produce (a) larger RMS and (b) a shorter threshold durations, when compared to the subgroup. The posterior distributions are shown in Figure \ref{fig:eeg_comp} for the SSVEP data, and in Figure \ref{fig:durations_comp} for the psychophysical data, which distributions color-coded according to conditional probability. For both data sets our hypothesis is confirmed: For the overwhelming majority of the 63 subgroup relationships, supergroups are more likely to produce larger symmetry-specific SSVEPs and shorter symmetry detection threshold durations, and in most cases the conditional probability of this happening is extremely high.

We also ran a control analysis using (1) odd-harmonic SSVEP data from a six-electrode ROI over parietal cortex (see Supplementary Figure 1.1) and (2) even-harmonic SSVEP data from the same occipital ROI that was used in our primary analysis. By comparing these two control analysis to our primary SSVEP analysis, we can address the specify of our effects in terms of location (occipital cortex vs parietal cortex) and harmonic (odd vs even). For both control analyses (plotted in Supplementary Figures 3.3 and 3.4), the correspondence between data and subgroup relationships was substantially weaker than in the primary analysis. We can quantify the strength of the association between the data and the subgroup relationships, by asking what proportion of subgroup relationships that reach or exceed a range of probability thresholds. This is plotted in Figure \ref{fig:roc_style}, for our psychophysical data, our primary SSVEP analysis and our two control SSVEP analyses. It shows that odd-harmonic SSVEP data from the occipital ROI and symmetry detection threshold durations both have a strong association with the subgroup relationships such that a clear majority of the subgroups survive even at the highest threshold we consider ($p(\Delta>0|data)>0.99$). The association is far weaker for the two control analyses.

@@

\textcolor{ForestGreen}{The current study uses 16 distinct wallpaper groups, while previous neuroimaging studies focused on a subset of 4 \citep{RN1725,RN1959}. This represents a significant conceptual advance, because it makes it possible to investigate the complete subgroup hierarchy among the 17 groups and ask to what extent the hierarchy is reflected in brain activity. Our data} provide a description of the visual system’s response to the complete set of symmetries in the two-dimensional plane. 
\textcolor{ForestGreen}{We do not} independently measure the response to \textit{P1}, but because each of the 16 other groups produce non-zero odd harmonic amplitudes (see Figure \ref{fig:summary}), we can conclude that the relationships between P1 and all other groups, where \textit{P1} is the subgroup, are also preserved by the visual system. The subgroup relationships are in many cases not obvious perceptually, and most participants had no knowledge of group theory. Thus, the visual system’s ability to preserve the subgroup hierarchy does not depend on explicit knowledge of the relationships. \textcolor{ForestGreen}{Previous brain-imaging studies have found evidence of parametric responses with the number of reflection symmetry folds \cite{keefe_2018, Sasaki_2005, makin_2016} and with the order of rotation symmetry \cite{RN1725}. Our study is the first demonstration that the brain encodes symmetry in this parametric fashion across every possible combination of different \textit{symmetry types}, and that this parametric encoding is also reflected in behavior.} Previous behavioral experiments have shown that although naïve observers can distinguish many of the wallpaper groups \citep{RN1253}, they tend to sort exemplars into fewer \textcolor{ForestGreen}{(4-12) sets than the number of wallpaper groups, often placing exemplars from different wallpaper groups in the same set \citep{RN172}. The two-interval forced choice approach we use in the current psychophysical experiment makes it possible to directly compare symmetry detection thresholds to the subgroup hierarchy, and reveals that not only can the 17 wallpaper groups be distinguished based on behavioral data, behavior largely follows the subgroup hierarchy.}

\textcolor{ForestGreen}{A large literature exists on the \textit{Sustained Posterior Negativity} (SPN), a characteristic negative-going waveform that is known to reflect responses to symmetry and other forms of regularity and structure \citep{makin_2016}. The SPN scales with the proportion of reflection symmetry in displays that contain a mixture of symmetry and noise \cite{makin_formation_2020, palumbo_scaling_2015}, and both reflection, rotation and translation can produce a measurable SPN \cite{makin_2013}. It has recently been demonstrated that a holographic model of regularity \citep{van_der_helm_1996}, can predict both SPN amplitude \citep{makin_2016} and perceptual discrimination performance \citep{nucci_2007} for dot patterns that contain symmetry and other types of regularity. The available evidence suggests that the SPN and our SSVEP measurements are two distinct methods for isolating the same symmetry-related brain response: When observed in the time-domain, the symmetry-selective odd-harmonic responses produce similarly sustained waveforms (see Figure \ref{fig:summary}), odd-harmonic SSVEP responses can be measured for dot patterns similar to those used to measure the SPN \citep{RN1954}, and the one event-related study on the wallpaper groups also found SPN-like waveforms \citep{RN1959}. Future work should more firmly establish the connection and determine if the SPN can capture similarly precise symmetry responses as the SSVEPs presented here. It would also be worthwhile to ask if and how \textit{W} can computed for our random-noise based wallpaper textures where combinations of symmetries tile the plane.}

We observe a reliable correlation between our brain imaging and psychophysical data. This suggests that the two measurements reflect the same underlying symmetry representations in visual cortex. \textcolor{ForestGreen}{It should be noted that the correlation is relatively modest ($R^2 = 0.44$). This may be partly due to the fact that different individuals participated in the two experiments. It may also be related to the fact that participants where not doing a symmetry-related task during the SSVEP experiment, but instead monitored the stimuli for brief changes in contrast that occured twice per trial (see Methods). Previous brain imaging studies have found enhanced reflection symmetry responses when participants performed a symmetry-related task \citep{makin_formation_2020, Sasaki_2005, keefe_2018}. It is possible that adding a symmetry-related task to our SSVEP experiment would have produced measurements that reflected subgroup relationships to an even higher extent than what we observed. On the other hand, our results are already close to ceiling (see Figure \ref{fig:roc_style}) and adding a symmetry-related task may simply enhance SSVEP amplitudes overall without improving the discriminality of individual groups, as has been observed for reflection by \cite{keefe_2018}. Task-driven processing may be important for detecting symmetries that have been subject to perspective distortion, as suggested by SPN measurements \citep{makin_conditions_2015} and somewhat less clearly in a subsequent functional MRI study \citep{keefe_2018}. Future work in which behavioral and brain imaging data are collected from the same participants, and task is manipulated in the SSVEP experiment, will help further establish the connection between the two measurements, and elucidate the potential contribution of task-related top-down processing to the current results.}

We also find an effect of index for both our brain imaging measurements and our symmetry detection thresholds. This means that the visual system not only represents the hierarchical relationship captured by individual subgroups, but also distinguishes between subgroups depending on how many times the subgroup is repeated in the supergroup, with more repetitions leading to larger pairwise differences. Our measured effect of index is relatively weak. This is perhaps because the index analysis does not take into account the \textit{type} of isometries that differentiate the subgroup and supergroup. The effect of symmetry type can be observed by contrasting the measured SSVEP amplitudes and detection thresholds for groups \textit{PM} and \textit{PG} in Figure \ref{fig:summary}. The two groups are comparable except \textit{PM} contains reflection and \textit{PG} contains glide reflection, and the former clearly elicits higher amplitudes and lower thresholds. An important goal for future work will be to map out how different symmetry types contribute to the representational hierarchy.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\linewidth]{../analysis/plots/model_roc_style.pdf}
\caption{This plot shows the proportion of subgroup relationships that satisfy \textcolor{ForestGreen}{$p(\Delta >0 | data) > x$ for the SSVEP data and $p(\Delta <0 | data) > x$ for the psychophysical data}. We can see that if we take $x = 0.95$ as our threshold, the subgroup relationships are preserved in 56/63 = 89\% and \textcolor{ForestGreen}{48/63 = 76\%} of the comparisons for the primary SSVEP and threshold duration datasets, receptively. This compares to the \textcolor{ForestGreen}{32/63= 51\%} and \textcolor{ForestGreen}{22/63 = 35\%} for the SSVEP control datasets.}
\label{fig:roc_style}
\end{figure}

@@

\subsection*{SSVEP Analysis}
Response waveforms were generated for each group by selective filtering in the frequency domain. For each participant, the average Fourier coefficients from the two sessions were averaged over trials and sessions. The SSVEP paradigm we used allowed us to separate symmetry-related responses from non-specific contrast transient responses. Previous work has demonstrated that symmetry-related responses are predominantly found in the odd harmonics of the stimulus frequency, whereas the even harmonics consist mainly of responses unrelated to symmetry, that arise from the contrast change associated with the appearance of the second image \citep{RN1954, RN1725}. This functional distinction of the harmonics allowed us to generate a single-cycle waveform containing the response specific to symmetry, by filtering out the even harmonics in the spectral domain, and then back-transforming the remaining signal, consisting only of odd harmonics, into the time-domain. For our main analysis, we averaged the odd harmonic single-cycle waveforms within a six-electrode region of interest (ROI) over occipital cortex (electrodes 70, 74, 75, 81, 82, 83). These waveforms, averaged over participants, are shown in Figure \ref{fig:summary}. The same analysis was done for the even harmonics and for the odd harmonics within a six electrode ROI over parietal cortex (electrodes 53, 54, 61, 78, 79, 86; see Supplementary Figure 1.1). The root-mean square values of these waveforms, for each individual participant, were used to determine whether each of the wallpaper subgroup relationships were preserved in the brain data.
